[dcpo_demsupport]

### 2020-06-26 paper/dcpo_demsupport.Rmd
add claassen_m5_theta, what @sammo3182 *really* needs to replicate the analysis

@@

```{r comparison_table}

>>>>

claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")

save(claassen_m5_theta, file = "data/claassen_m5_theta.rda")

@@

```{r comparison_table}
load("data/claassen_m5_x_pred.rda")

ivt_claassen <- DCPOtools::internal_validation_tests(claassen_input, claassen_m5_x_pred, "claassen")

# see https://github.com/fsolt/dcpo_article/blob/master/R/validation_table.R for more to add when we have it
